Titeltext

### 2018-07-26 thesis/paper/paper.tex
Added multi-value

>>>>

\subsection{Multi-value (Q21510857)}
The multi-value constraint specifies that the constrained property should appear in multiple statements of an item or none.

\begin{table}[H]
\caption{Multi-value constraint (Q21510857)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & item statement \\
\hline
Violation & \makecell{constrained item with exactly one constrained statement} \\
\hline
Dependency & all item statements \\
\hline
Rule features & count \\
\hline
\end{tabularx}
\end{table}

To model this constraint a count of statements using the constrained property per item would be needed. Then a violation would be any constrained item with a count of one for the constrained property. Since there is no need for arbitrarily large counts, but only for the difference between one and two, this could be solved explicitly.
